---
title: "Facebook Ad Targeting"
author: "Zetong Jin"
output: html_document
---


#1.Running a regression to get familar with the data
```{r}
data = read.csv("/Users/thomas/Desktop/predictive/Facebook Data.csv")
summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+factor(keywords)+factor(body)+ageMean, data = data))
```


#2. Regression did not work for a single value
```{r}
#summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+factor(keywords)+factor(body)+ageMean+date, data = data)) 
#Not working
```

# This regression did not work because there is only a single value for date.

#3.Show the Interpretation of the factor(category)General coefficient
```{r}
#Coefficient: -45.741606
```

#The factor(category)General coefficient implies that ads in the general category receive -45.7 fewer clicks per dollar than the baseline, which is cosmetics.

#4.Show the Interpretation of the ageMean coefficient
```{r}
#Coefficient: 2.6
```

#The ageMean coefficient implies that a one year increase in ageMean results in an increase of 2.6 clicks per dollar.

#5. Analysis the interaction between category and ageMean as independent variables 
```{r}
summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+factor(keywords)+factor(body)+ageMean+factor(category):ageMean, data = data))
#Ecom and ageMean Interaction coefficient: -0.36125 
#ageMean coefficient: 2.41
```

#The factor(category)eCom:ageMean coefficient means that, in the eCom category, an increase of 1 in ageMean results in 0.358 fewer clicks per dollar than in the cosmetics category.

#6. 
```{r}
# Interaction coefficient: -28.29490
# no interaction coefficient: -42.643506 
```

# The coefficient of factor(category)eCom increased from -42.60 to -28.38. In the initial regression, factor(category)eCom showed the effect of eCom for all consumers, while in this regression, this categorical variable only applies to consumers with an age of 0.

#7. 

```{r}
# old
Facebook <- read.csv('/Users/thomas/Desktop/predictive/Facebook Data.csv')
summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+ factor(keywords)+factor(body)+factor(ageMean)+factor(category)*factor(ageMean),data = Facebook))

# new
New <- read.csv('/Users/thomas/Downloads/HW2DataNew.csv')
summary(lm(clickPerDollar~factor(adType)+factor(category)+factor(placement)+ factor(keywords)+factor(body)+factor(ageMean)+factor(category)*factor(ageMean),data = New))
```

# By comparing the old/new data, we can see that new ad is effective for the youngest age category and the eCom category